How to obtain the redshift distribution from probabilistic redshift estimates

### 2017-06-15 research/paper/draft-editing.tex
updating paer with fiducial mock data process

We present the two attributes of a probabilistic graphical model (PGM) for the redshift distribution $n(z)$: the directed acyclic graph of Fig. \ref{fig:pgm} and its mathematical interpretation below.  The assumption underlying the concept of photo-$z$ estimation is that each galaxy $i$ has some observed photometric data $\vec{d}_{i}$ (fluxes, magnitudes, or colors) that is drawn from a function of its redshift $z_{i}$, which is a parameter in this model.  The redshifts $\{z_{i}\}$ for all galaxies in a survey are random draws from the redshift distribution, a function which itself may be parametrized by hyperparameters comprising $\vec{\phi}$ that are shared among all $N$ galaxies in the survey.  From this perspective, $n(z)$ is itself a probability distribution for galaxy redshifts, i.e. $z_{i} \sim n(z)$.  Given a functional form of $n(z)$, we can say $n(z) = p(z_{i}|\vec{\phi})$ for any $i = 1, \dots, N$, determining that $n(z)$ is itself a likelihood.  This PGM enables hierarchical Bayesian inference; we will directly infer the posterior probability distribution $p(\vec{\phi} | \{\vec{d}_{i}\})$ of $\vec{\phi}$ given the observations.

\begin{figure}
	\begin{center}
		\includegraphics[width=0.5\textwidth]{pgm.png}
		\caption{This directed acyclic graph corresponds to a PGM for a hierarchical inference of $p(\vec{\phi}|\{\vec{d}_{i}\})$.  In this graph, all random variables are shown in circles, with observed random variables shown in shaded circles.  Relationships between variables are indicated by arrows from parameters to the variables distributed according to functions of them.  The box indicates that there are a number of copies of the relationships between boxed parameters, each independent of all others.  The hyperparameters comprising $\vec{\phi}$, which define $n(z)$, are at the top.  Independently drawn from a function of the hyperparameters $\vec{\phi}$ are galaxy redshifts $\{z_{i}\}$ below.  The observed galaxy photometry $\{\vec{d}_{i}\}$, shown in shaded circles, is determined by the redshifts above.}
	\label{fig:pgm}
	\end{center}
\end{figure}

@@

@@

@@

In this test, we choose the true $n(z)$ of Fig. \ref{fig:featured}, which has nontrivial structure.

\begin{figure}
	\begin{center}
		%\includegraphics[width=0.5\textwidth]{pgm.png}
		\caption{[plot of a highly featured (delta function or multimodal?) true $n(z)$]}
		\label{fig:featured}
	\end{center}
\end{figure}

>>>>

The directed acyclic graph of Fig. \ref{fig:pgm} represents a probabilistic graphical model for hierarchical inference of $n(z)$, the mathematical interpretation of which will be presented below.

\begin{figure}
	\begin{center}
% 		\includegraphics[width=0.5\textwidth]{pgm.png}
		\caption{\textbf{Replace \texttt{daft} version with more polished \texttt{tikz} version.}}
%		\caption{This directed acyclic graph corresponds to a PGM for a hierarchical inference of $p(\vec{\theta}|\{\vec{d}_{i}\})$.  In this graph, all random variables are shown in circles, with observed random variables shown in shaded circles.  Relationships between variables are indicated by arrows from parameters to the variables distributed according to functions of them.  The box indicates that there are a number of copies of the relationships between boxed parameters, each independent of all others.  The hyperparameters $\vec{\theta}$ representing $n(z)$ are at the top.  Independently drawn from a function of the hyperparameters $\vec{\theta}$ are galaxy redshifts $\{z_{i}\}$ below.  The observed galaxy photometry $\{\vec{d}_{i}\}$, shown in shaded circles, is determined by the redshifts above.}
	\label{fig:pgm}
	\end{center}
\end{figure}

\textbf{Math from \texttt{prob-z} version will go here.}

@@

\begin{enumerate}
	\item Choose a true $n(z)$ that is a continuous function with known parameters $\vec{\theta}$.
	\item Sample the true $n(z)$ to create a catalog of $N$ true redshifts $z_{i}$.
	\item Choose a true intrinsic scatter $\sigma$, and sample Gaussians $p(z'_{i} | z_{i}, \sigma) = \mathcal{N}(z_{i}, \sigma)$ to get "observed" redshifts $z'_{i}$ defining Gaussian likelihoods $p(\vec{d}_{i} | z'_{i}, \sigma) = \mathcal{N}(z'_{i}, \sigma)$.
	\item Choose a parametrization and the parameters $\vec{\phi}^{*}$ of the interim prior.
	\item Create interim posteriors $p(z_{i} | \vec{d}_{i}, \vec{\phi}^{*}) = p(\vec{d}_{i} | z_{i})\ p(z_{i} | \vec{\phi}^{*})$
\end{enumerate}

@@

\subsubsection{Featureless $n(z)$}
\label{sec:smooth}

In this test, we choose a weakly featured true $n(z)$ of Fig. \ref{fig:smooth} with a smooth, unimodal shape.

\begin{figure}
	\begin{center}
		%\includegraphics[width=0.5\textwidth]{pgm.png}
		\caption{[plot of a weakly featured true $n(z)$, probably SDSS interim prior]}
		\label{fig:featured}
	\end{center}
\end{figure}

In this test, we choose the true $n(z)$ of Fig. \ref{fig:featured} with nontrivial structure.

\begin{figure}
	\begin{center}
		%\includegraphics[width=0.5\textwidth]{pgm.png}
		\caption{[plot of a highly featured, multimodal true $n(z)$]}
		\label{fig:featured}
	\end{center}
\end{figure}

This featured true $n(z)$ will henceforth be referred to as the fiducial $n(z)$

@@
